Figures for 3-D printed oxygen devices

### 2015-02-06 publishing/latex/plos_template.tex
added whole render to figure 1 and figure labels, fixed bracket in manuscript

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
Microfluidic 3D printed devices have been used in XYZ.
Many quintessential microfluidic devices and features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014}.
3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014]. 
Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
Printing is currently limited in choice of materials compatable with the process and include many proprietary fomulations, regardless these have been sucessfully used in a variety of applications.
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.

>>>>

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
Microfluidic 3D printed devices have been used in XYZ.
Many quintessential microfluidic devices and features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{Au2014, Shallan2014}.
3D printed devices have been used for inexpensive and high-throughput reactionware,\cite{Kitson2014}, for a measureing dopamine and ATP levels in biological samples\cite{Erkal2014}
Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014, Chen2014, Shallan2014,Erkal2014,Kitson2014}. 
Printing is currently limited in choice of materials compatable with the process and include many proprietary fomulations, regardless these have been sucessfully used in a variety of applications.
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
